---
title: "Regression"
author: "Anna Yeaton"
date: "Fall 2019"
output:
  html_document:
    df_print: paged
fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = T)
```

# Lab Section

In this lab, we will go over regression. We will be using the caret package in R. https://topepo.github.io/caret/train-models-by-tag.html

# Perfomance Metrics 

## Residual 

Deviation of the observed value to the estimated value (sample mean)
$$residual=y_i - \hat{y_i}$$
where $\hat{y_i}$ is the estimated value

## Mean Squared Error (MSE)

$$MSE=\frac{1}{n}\sum_{i=1}^{n}(y_i - \hat{y_i})^2$$

## Root Mean Squared Error (RMSE)
Same units as original data.

$$RMSE=\sqrt{MSE}$$

## L2 regularization : Ridge regression. Regularize by adding the sum of the coefficients, squared, to the function. 

$$Ridge Regression=\sum_{i=1}^{n}(y_i - w_0 - \sum_{j=1}^{p}w_jx_{ij})^2 + \lambda\sum_{j=1}^p(w_j)^2$$

## L1 regularization : Lasso Regression. Regularize by adding the sum of the absolute value of the coefficients to the model. Coefficient estimates may be pushed to zero -- Lasso can perform variable selection

$$Lasso Regression=\sum_{i=1}^{n}(y_i - w_0 - \sum_{j=1}^{p}w_jx_{ij})^2 + \lambda\sum_{j=1}^p|w_j|$$


\newpage

### The broad steps of Machine learning in R. 

1. Split the data into training and test. Set test aside. 

2. Fit a good model to the training data. 

3. See how your model did on the training data.

4. Test how your model performs on the test data. 

# Regression

```{r, include=FALSE}
library(caret)
library(MASS)
library(ggplot2)
library(dplyr)
library(ggfortify)
library(glmnet)

#Mauna Loa CO2 concentrations
data(airquality)
```


1. Split data into training and test set (75% in train set, 25% in test set)

```{r}
#setting seed to reproduce random selection
set.seed(123)
train_ind <- sample(seq_len(nrow(airquality)), size = floor(0.75 * nrow(airquality)))

#defining train and test sets
train <- airquality[train_ind, ]
test <- airquality[-train_ind, ]
```


### Linear Regression

* Assumes a linear relationship. 
* Independent variables should not be correlated (no mulitcollinearity)
* The number of observations should be greater than the number of independent variables.


$$RSS=\sum(y_i - \hat{y_i})^2$$
We will predict the response of the Temperature based on Wind. 

This is the data we will fit a linear model to. 
```{r}
ggplot(data = train) +
   geom_point(aes(x=Wind, y=Temp)) +
   theme_bw()
```

2. Create and fit a linear model to predict Temperature from Wind using the training set

```{r}
help(train)

linear_regression <- train(Temp ~ Wind, data = train, method = "lm")
```


3. Vizualize how your model performed on the train data by plotting the regression line on top of the train data points. 
```{r}
pred <- predict(linear_regression, train)
pred <- data.frame(pred = pred, Wind = train$Wind)

ggplot(data = pred)+
  geom_line(aes(x = Wind, y = pred))+
  geom_point(data = train, aes(x=Wind, y = Temp))
```


4. Explore how the model performs on the test data. For Linear Regression:

* The residuals should be close to zero.
* There should be equal variance around the regression line (homoscedasticity).
* Residuals should be normally distributed.
* Independent variables and residuals should not be correlated.

4 a) See how the model performs on the test data
```{r}
help(predict)
linear_predict <- predict(linear_regression, newdata=test)
```

4 b) Look at the residuals. Are they close to zero?
```{r}
#look at the median residual value. Close to zero is best
help(summary)
summary(linear_regression, newdata=test)
```
Median residual is somewhat close to zero, but min and max are not, suggesting that there is quite a bit of variance in the data that is not captured by the model, but that over and underestimation are about equal.

4 c) Plot predicted temperature vs observed temperature. A strong model should show a strong correlation
```{r}
#plot of predicted and actual temperature
plot(linear_predict, test$Temp,
      xlab="predicted",ylab="actual")
abline(a=0,b=1)
```

4 d) Visualize the predicted values in relation to the real data points. Look for homoscedasticity
```{r}
# Extract coefficients from the model
coeff <- summary(linear_regression)$coefficients
coeff

# plot the regression line on the predicted values
pred_test <- predict(linear_regression, test)
pred_test <- data.frame(pred = pred_test, Wind = test$Wind)

ggplot(data = pred_test)+
  geom_line(aes(x = Wind, y = pred))+
  geom_point(data = pred_test, aes(x=Wind, y = pred))

# plot the original test values
ggplot(data = pred)+
  geom_line(aes(x = Wind, y = pred))+
  geom_point(data = test, aes(x=Wind, y = Temp))
```

4 e) Residuals should be normally distributed. Plot the density of the residuals
```{r}
plot(density(resid(linear_regression)))
#residuals_lin <- residuals(linear_regression)

#ggplot(data=residvpredict) +
#  geom_density(aes(residual))
```


4 f) Independent variables and residuals should not be correlated
```{r}
cor.test(train$Wind, resid(linear_regression))
```


### Linear Regression with Regularization

5. Create a linear model using L1 or L2 regularization to predict Temperature from Wind and Month variables. Plot your predicted values and the real Y values on the same plot. 

```{r}
#subsetting data for variables of interest
airquality_month <- airquality[c(3:5)]

#setting seed to reproduce random selection
set.seed(123)
train_ind_month <- sample(seq_len(nrow(airquality_month)), size = floor(0.75 * nrow(airquality_month)))

#defining train and test sets
train_month <- airquality_month[train_ind_month, ]
test_month <- airquality_month[-train_ind_month, ]

#defining preditor and prediction variables
x <- model.matrix(Temp ~ ., train_month)[,-1]
y <- train_month$Temp

#finding the best lamda
set.seed(123) 
cv <- cv.glmnet(x, y, alpha = 0)

#fitting model to training data
ridge_regression <- glmnet(x, y, alpha = 0, lambda = cv$lambda.min)
#using model to predict on test data
ridge_regression_test <- model.matrix(Temp ~., test_month)[,-1]
predictions <- ridge_regression %>% predict(ridge_regression_test)

#plotting predicted temp and actual temp
plot(predictions, test_month$Temp,
      xlab="Predicted Temperature",ylab="Actual Temperature")
```


